Choosing and rating harmonies

### 2020-08-14 main.Rmd
refining structure

# Background

@@

## Computing distances

@@

@@

## Threshold definition for test through permutation test

@@

## Level and power of the test

@@

## Scenario 1: Simulated same normal distributions for all combinations of categories for all harmony pairs.

@@

## Scenario 2: Simulated different distributions for all combinations of categories for harmony pairs for few levels.

@@

## Scenario 3: Simulated different distributions for all combinations of categories for all harmony pairs with many levels.

@@

@@

@@

>>>>

@@

## Distance between distributions

@@

## Algorithm

\noindent The algorithm employed for computing MMPD is summarized as follows:
<!-- Algorithm -->

<!-- 1. Suppose $C_i$ and $C_2$ are two cyclic granularities such that $C_i$ maps index set to a set $\{A_1, A_2, A_3, \dots, A_l$\}, and $C_2$ maps index set to a set $\{B_1, B_2, B_3, \dots, B_m$\} and $v$ is the measured variable. Hence for each combination ($A_k$, $B_l$), we have the time series variable $v_{ij} \subseteq v$, $\forall i = {1, 2, \dots, l}$ and $\forall j = {1, 2, \dots, m}$ -->

- **Input:** Data corresponding to all harmony pairs, i.e., data sets of the form $(C_i, C_j, v)$ 
$\forall i, j \in N_C$  
- **Output:** MMPD (Median Maximum Pairwise Distances) measuring the average variation across different levels of $C_i$ and $C_j$ $\forall i, j \in N_C$

1. Fix harmony pair $(C_i, C_j)$.

2. Fix $k$. Then there are $L$ groups corresponding to level $A_k$ of $C_i$.

3. Compute  $m = \binom{L}{2}$ pairwise distances between distributions of $L$ unordered levels and $m = L-1$ pairwise distances for $L$ ordered categories.

4. Identify maximum within the $m$ computed distances.

5. Compute normalized maximum distance ($NM$) using appropriate norming constants.
<!--so that the distribution of the normalized maximum converges to a Gumbel distribution as $m\rightarrow\infty$.-->

6. Use Steps 1-5 to compute normalized maximum distance for $\forall k \in  \{1, 2, \ldots, K\}$.

7. Compute MMPD = median $(NM_1, NM_2, \dots, NM_K)$/log($K$).

8. Repeat Steps 1 to 7 for all harmony pairs.

### Interpreting the test statistic

@@

## Algorithm for threshold

@@

## Level and power

@@

### Scenario 1: Simulated same normal distributions for all combinations of categories for all harmony pairs.

@@

### Scenario 2: Simulated different distributions for all combinations of categories for harmony pairs for few levels.

@@

### Scenario 3: Simulated different distributions for all combinations of categories for all harmony pairs with many levels.

@@

### Scenario 4: Simulated different distributions for all combinations of categories for all harmony pairs with many levels - very different distribution across x-axis

@@

### Scenario 5: Simulated different distributions for all combinations of categories for all harmony pairs with many levels - very different distribution across facets

@@

<!-- *Conclusion*:  -->
